### 2024-08-25 paper.tex
more about dimensions

\begin{corollary}\label{alternative_bs_two}
    \(B_{I, (\rho_i)}\) is the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
    \begin{itemize}
        \item For all \(k \in \{1, ..., r\}\), \(p_{i_k} = \rho_{i_k}\).
        \item For \(i \notin I\),
        \begin{itemize}
            \item If \(\lambda_i \geq q_{i_0} + p_{i_1}\), then \(p_i \leq \lambda_i - q_{i_0}\).
            \item If there is \(k \in \{0, ..., r\}\) with \(q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\), then \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
            \item If \(q_{i_r} + p_{i_{r + 1}} > \lambda_i\), then \(p_i \leq p_{i_{r + 1}}\).
        \end{itemize}
    \end{itemize}
\end{corollary}
\begin{proof}
    Both \(q_{i_k}\) and \(p_{i_k}\) are decreasing as \(k\) increases, so this follows directly from \cref{alternative_bs_one}.
    (Note that \(p_i \leq \lambda_i - q_{i_k}\) iff \(q_{i_k} \leq q_i\).)
\end{proof}

\begin{corollary}\label{bs_iso}
    \[B_{I, (\rho_i)} \cong \prod_{k = 1}^r (\mathbb{C}^{\rho_{i_k} - 1} \times (\mathbb{C} \setminus \{0\})) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} \mathbb{C}^{\lambda_i - q_{i_0}} \times \prod_{k = 0}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}}\mathbb{C}^{\min(p_{i_k}, \lambda_i - q_{i_k})}\]
\end{corollary}
\begin{proof}
    Here I use the notation \(x \times y = (x, y)\), and so on.
    The isomorphism sends \(b \in B_{I, (\rho_i)}\) to 
    \[\prod_{k = 1}^{r}(b_{i_k1},..., b_{i_k\rho_{i_k}}) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (b_{i1}, ..., b_{i, \lambda_i - q_{i_0}}) \times\]
    \[\prod_{k = 0}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (b_{i1}, ..., b_{i,\min(p_{i_k}, \lambda_i - q_{i_k})}).\]
    \cref{alternative_bs_two} tells us that this is an isomorphism.
\end{proof}

\begin{corollary}\label{bs_dim}
    \[\dim B_{I, (\rho_i)} = \sum_{i : \lambda_i \geq q_{i_0} + \rho_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 0}^r \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k}).\]
\end{corollary}
\begin{proof}
    Immediate from \cref{bs_iso}.
\end{proof}

@@

\begin{lemma}
    \(\gamma([\mu_1, ..., \mu_l]) = \gamma([0, \lambda_1, ..., \lambda_k]) - something\).
\end{lemma}
\begin{proof}
    Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_k]\).
    Note that \(\mu = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., ..., q_{i_r} + p_{i_{r + 1}}, ...]\).
    Let \(L'\) be the result of taking \(\mu\) and, for each \(x\), replacing one occurence of \(q_{i_x} + p_{i_{x + 1}}\) by \(q_{i_x} + p_{i_x}\); that is,
    \(L' = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}]\).
    Note that we get from \(\mu\) to \(L'\) by just moving each \(p_{i_k}\) to the right by \(1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}\) slots.
    So,
    \[\gamma(L') - \gamma(\mu) = \sum_{k = 1}^r p_{i_{k + 1}} (1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}) = \]
    \[\sum_{k = 1}^r p_{i_k} \cdot \#\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}.\]
    Now we consider how to get from \(L'\) to \(L\).
    First we shift \(q_{i_0}\) to the left by \(\#\{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}\}\) slots.
    Then we leave \(q_{i_0}\) in place and sort the rest of the list.
    This entails shifting each \(q_{i_x} + p_{i_x}\) to the left by \(\#\{i \notin I : q_{i_x} + p_{i_x} > \lambda_i \geq q_{i_x} + p_{i_{x + 1}}\}\) slots.
    Shifting \(q_{i_x} + p_{i_x}\) to the left one slot, by swapping it with \(\lambda_i\), changes the value of \(\gamma\) by \(\lambda_i - (q_{i_x} + p_{i_x})\).
    To go from \(L'\) to \(s(L')\), we can just make these swaps repeatedly.  
    So,
    \[\gamma(L) - \gamma(L') = \]
    \[\sum_{i \notin I : q_{i_0} + p_{i_1} > \lambda_i \geq q_{i_0}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i \notin I : q_{i_k} + p_{i_{k + 1}} > \lambda_i \geq q_{i_k} + p_{i_k}\}} (\lambda_i - (q_{i_k} + p_{i_k})).\]
    TODO: the thing above would be cleaner if \(p_{i_0} := 0\).
    \par Now,
    \begin{align*}
        \gamma(L) - \gamma(\mu) & = \\
        [\gamma(L) - \gamma(L')] + [\gamma(L') - \gamma(\mu)] & = \\
    \end{align*}    
\end{proof}

\begin{lemma}
    \(U_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times X_\mu\).
\end{lemma}
\begin{proof}
    For \(b \in B_{I, (\rho_i)}\), let \(P_b\) be the change-of-basis matrix, with columns given by the Jordan basis of the previous lemma, so that \(J(\mu) = P_b^{-1} A_{0,b} P_b\).
    From looking at the Jordan basis of the previous lemma (the basis can be expressed in terms of \(A, \lambda, e_{ij}, f_i, I, \rho_i, b\)), it is clear that the map \(P : B_{I, (\rho_i)} \to \GL_{m + n}\), given by \(b \mapsto P_b\), is algebraic.
    \par Now, we remark that the Springer fiber at \(A_{0,b}\) is simply \(\{P_b U : U \in X_\mu\}\).
    This gives us the isomorphism \(B_{I, (\rho_i)} \times X_\mu \to U_{I, (\rho_i)}\).
    \[(b, U) \mapsto (P_b J(\mu) P_b^{-1}, P_b U),\]
    with inverse
    \[(A_{0,b}, U) \mapsto (b, P_b^{-1} U).\]
\end{proof}

>>>>

\begin{corollary}\label{alternative_bs_two}
    \(B_{I, (\rho_i)}\) is the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
    \begin{itemize}
        \item For all \(k \in \{1, ..., r\}\), \(p_{i_k} = \rho_{i_k}\).
        \item For \(i \notin I\),
        \begin{itemize}
            \item If \(\lambda_i \geq q_{i_0} + p_{i_1}\), then \(p_i \leq \lambda_i - q_{i_0}\).
            \item If there is \(k \in \{1, ..., r\}\) with \(q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\), then \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
            \item If \(q_{i_r} + p_{i_{r + 1}} > \lambda_i\), then \(p_i \leq p_{i_{r + 1}}\).
        \end{itemize}
    \end{itemize}
\end{corollary}
\begin{proof}
    Both \(q_{i_k}\) and \(p_{i_k}\) are decreasing as \(k\) increases, so this follows directly from \cref{alternative_bs_one}.
    (Note that \(p_i \leq \lambda_i - q_{i_k}\) iff \(q_{i_k} \leq q_i\).)
\end{proof}

\begin{corollary}\label{bs_iso}
    \[B_{I, (\rho_i)} \cong \prod_{k = 1}^r (\mathbb{C}^{\rho_{i_k} - 1} \times (\mathbb{C} \setminus \{0\})) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} \mathbb{C}^{\lambda_i - q_{i_0}} \times \prod_{k = 1}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}}\mathbb{C}^{\min(p_{i_k}, \lambda_i - q_{i_k})}\]
\end{corollary}
\begin{proof}
    Here I use the notation \(x \times y = (x, y)\), and so on.
    The isomorphism sends \(b \in B_{I, (\rho_i)}\) to 
    \[\prod_{k = 1}^{r}(b_{i_k1},..., b_{i_k\rho_{i_k}}) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (b_{i1}, ..., b_{i, \lambda_i - q_{i_0}}) \times\]
    \[\prod_{k = 1}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (b_{i1}, ..., b_{i,\min(p_{i_k}, \lambda_i - q_{i_k})}).\]
    \cref{alternative_bs_two} tells us that this is an isomorphism.
\end{proof}

\begin{corollary}\label{bs_dim}
    \[\dim B_{I, (\rho_i)} = \sum_{i : \lambda_i \geq q_{i_0} + \rho_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^r \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k}).\]
\end{corollary}
\begin{proof}
    Immediate from \cref{bs_iso}.
\end{proof}

@@

\begin{lemma}
    \[\gamma([\mu_1, ..., \mu_l]) = \gamma([0, \lambda_1, ..., \lambda_k]) - \] 
    \[\left[\sum_{i : \lambda_i \geq q_{i_0} + \rho_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^r \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k})\right].\]
\end{lemma}
\begin{proof}
    Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_k]\).
    Note that \(\mu = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., ..., q_{i_r} + p_{i_{r + 1}}, ...]\).
    Let \(L'\) be the result of taking \(\mu\) and, for each \(x\), replacing one occurence of \(q_{i_x} + p_{i_{x + 1}}\) by \(q_{i_x} + p_{i_x}\); that is,
    \(L' = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}]\).
    Note that we get from \(\mu\) to \(L'\) by just moving each \(p_{i_k}\) to the right by \(1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}\) slots.
    So,
    \[\gamma(L') - \gamma(\mu) = \sum_{k = 1}^r p_{i_k} (1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}) = \]
    \[\sum_{k = 1}^r p_{i_k} \cdot \#\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}.\]
    Now we consider how to get from \(L'\) to \(L\).
    First we shift \(q_{i_0}\) to the left by \(\#\{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}\}\) slots.
    Then we leave \(q_{i_0}\) in place and sort the rest of the list.
    This entails shifting each \(q_{i_x} + p_{i_x}\) to the left by \(\#\{i \notin I : q_{i_x} + p_{i_x} > \lambda_i \geq q_{i_x} + p_{i_{x + 1}}\}\) slots.
    Shifting \(q_{i_x} + p_{i_x}\) to the left one slot, by swapping it with \(\lambda_i\), changes the value of \(\gamma\) by \(\lambda_i - (q_{i_x} + p_{i_x})\).
    To go from \(L'\) to \(s(L')\), we can just make these swaps repeatedly.  
    So,
    \[\gamma(L) - \gamma(L') = \]
    \[\sum_{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i \notin I : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (\lambda_i - (q_{i_k} + p_{i_k})).\]
    \par Now,
    \begin{align*}
        \gamma(L) - \gamma(\mu) & = \\
        [\gamma(L) - \gamma(L')] + [\gamma(L') - \gamma(\mu)] & = \\
        \left[\sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (\lambda_i - (q_{i_k} + p_{i_k}))\right] & + \\
        \left[\sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} p_{i_k}\right] & = \\
        \sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_k}\}} p_{i_k} & + \\
        \sum_{k = 1}^s \sum_{i : q_{i_k} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}} (\lambda_i - q_{i_k}) & = \\
        \sum_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i : q_{i_{k - 1} + p_{i_k}} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} \min(p_{i_k}, \lambda_i - q_{i_k}) & .
    \end{align*}    
\end{proof}

\begin{lemma}\label{u_i_rho_iso}
    \(U_{I, (\rho_i)} \cong B_{I, (\rho_i)} \times X_\mu\).
\end{lemma}
\begin{proof}
    For \(b \in B_{I, (\rho_i)}\), let \(P_b\) be the change-of-basis matrix, with columns given by the Jordan basis of the previous lemma, so that \(J(\mu) = P_b^{-1} A_{0,b} P_b\).
    From looking at the Jordan basis of the previous lemma (the basis can be expressed in terms of \(A, \lambda, e_{ij}, f_i, I, \rho_i, b\)), it is clear that the map \(P : B_{I, (\rho_i)} \to \GL_{m + n}\), given by \(b \mapsto P_b\), is algebraic.
    \par Now, we remark that the Springer fiber at \(A_{0,b}\) is simply \(\{P_b U : U \in X_\mu\}\).
    This gives us the isomorphism \(B_{I, (\rho_i)} \times X_\mu \to U_{I, (\rho_i)}\).
    \[(b, U) \mapsto (P_b J(\mu) P_b^{-1}, P_b U),\]
    with inverse
    \[(A_{0,b}, U) \mapsto (b, P_b^{-1} U).\]
\end{proof}

\begin{corollary}\label{u_i_rho_irred_and_dim}
    The 
    \(U_{I, (\rho_i)}\) is irreducible, and its dimension is \(\gamma([0, \lambda_1, ..., \lambda_k])\).
\end{corollary}
\begin{proof}
    Irreducibility follows from \cref{u_i_rho_iso}, since \(B_{I, (\rho_i)}\) is irreducible (by \cref{bs_iso}), as is \(X_\mu\).
    To get the dimension, we add the dimension of \(B_{I, (\rho_i)}\) to the dimension of \(X_\mu\).
    The dimension of \(X_\mu\) is 
\end{proof}
